Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-03 draft.Rmd
Update draft.Rmd

Countries differ in their rates of job mobility. Significant attention has been paid to the role of employment protection legislation in explaining this, however, the rewards tied to job mobility likely play a role in determining job mobility. This article has two aims. First we compare the effects of quits and promotions on earnings growth. Second, we consider their effects in two institutional settings (Germany and the UK). Studies exploring the effects of job mobility are rare, studies which compare and contrast these in separate frameworks, or capitalisms, are more rare still.

We offer two findings. First, internal and external mobility types are fundamentally different mechanisms for improving earnings, depsite both being labeled "voluntary". Internal promotions reward workers better than quits between firms. In both countries, promotions and internal movements offer a higher premium to workers than quits and external movements. Three, the effect of promotions is larger in Germany than the UK. This suggests British workers must experience several internal changes before seeing substantial gain, while German workers see substantial gain after fewer internal changes. Workers are mobile in both countries, however, the high premium tied to internal mobility in Germany may act as an incentive to commit to the firm. Findings challenge the narrative of mobile and “boundaryless” markets, and question whether mobile markets are inherently “good” for workers.

>>>>

Countries differ in their rates of job mobility. Researcher have paid significant attention to employment protection legislation in explaining this, however, rewards tied to job mobility may play a strong role also. This article has two aims. First we compare the effects of quits and promotions on earnings growth. Second, we consider their effects in two institutional settings (Germany and the UK). Studies exploring the effects of job mobility are rare, studies which compare and contrast these in separate frameworks, or capitalisms, are more rare still.

We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both being "voluntary" forms of movement. Internal promotions reward workers better than quits between firms. In both countries, promotions and internal movements offer a higher premium to workers than quits and external movements. Three, the effect of promotions is larger in Germany than the UK. This suggests British workers must experience several internal changes before seeing substantial gain, while German workers see substantial gain after fewer internal changes. Workers are mobile in both countries, however, the high premium tied to internal mobility in Germany may act as an incentive to commit to the firm. Findings challenge the narrative of mobile and “boundaryless” markets, and question whether mobile markets are inherently “good” for workers.
